---
name: "Gertjan"
surname: "van den Bos"
position: "Data Scientist"
address: "Utrecht area - The Netherlands"
phone: "+31 6 27576101"
email: "gertjanvdbos@gmail.com"
github: "G3rtjan"
linkedin: "gertjanvdbos"
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "0395DE"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Skills

## Data Science

* Time Series, Forecasting, Anomaly Detection, Classification, Regression, Graph Analysis, Data Wrangling, Data Visualization, Dashboarding, Process Automation

## Languages

* R (advanced): i.a. dplyr, tidyr, ggplot2, shiny, forecast, caret, purrr, data.table
* Python (intermediate): i.a. pandas, numpy, sklearn, dash, TensorFlow, Keras, PySpark

## Applications

* RStudio, Jupyter Notebook, Git Bash, SQL Developer, SAS EG

# Experience

```{r}
# Define information on Financial Crime & RegTech Analytics
ING_fin_crime_and_regtech <- c("Data Scientist", "ING Bank N.V. - Financial Crime & RegTech Analytics", "2019 - present", "Amsterdam")
# Define information on Finance Analytics
ING_finance <- c("Data Scientist", "ING Bank N.V. - Finance Analytics", "2016 - 2019", "Amsterdam")
# Define information on ING Arrears department
ING_arrears <- c("Data Scientist", "ING Bank N.V. - Arrears Department", "2014 - 2015", "Amsterdam")
# Define information on ING Arrears department internship
ING_arrears_intern <- c("Graduate Intern", "ING Bank N.V. - Arrears Department", "2013 - 2014", "Amsterdam")
# Combine all information
tribble(
  ~ role, ~ company, ~ dates, ~ loc, ~ details,
    # ING financial crime & regtech
  ING_fin_crime_and_regtech[1], ING_fin_crime_and_regtech[2], ING_fin_crime_and_regtech[3], ING_fin_crime_and_regtech[4],
    "Part of a medium sized team of data scientists (15 FTE), working on projects within the (global) ING Financial Crime & Regtech domain",
  # ING finance
  ING_finance[1], ING_finance[2], ING_finance[3], ING_finance[4],
    "Involved in setting up the Finance Analytics Center-of-Expertise, to exploit data for improved financial decisions",
  ING_finance[1], ING_finance[2], ING_finance[3], ING_finance[4],
    "Part of a small team of data scientists (2-3 FTE), working as internal consultants on projects within the (global) ING Finance domain",
  ING_finance[1], ING_finance[2], ING_finance[3], ING_finance[4],
    "Development of a pipeline of R packages for data cleaning, time series forecasting and interactive dashboarding for end-users",
  ING_finance[1], ING_finance[2], ING_finance[3], ING_finance[4],
    "Support the ING Finance Academy to provide training to Finance colleagues in Amsterdam, Brussels, Frankfurt and New York",
  # ING arrears
  ING_arrears[1], ING_arrears[2], ING_arrears[3], ING_arrears[4],
    "Development and incremental improvement of several customer classificaton models, using machine learning methods in R",
  ING_arrears[1], ING_arrears[2], ING_arrears[3], ING_arrears[4],
    "Performing data analysis for the testing of new propositions for customers in arrears, using A-B testing in pilots",
  ING_arrears[1], ING_arrears[2], ING_arrears[3], ING_arrears[4],
    "Creating new interactive tools for the call employees to increase insight into the financial situation of individual customers",
  # ING arrears intern
  ING_arrears_intern[1], ING_arrears_intern[2], ING_arrears_intern[3], ING_arrears_intern[4],
    "Research for my MSc Thesis on the application of Continuous Risk Management to reduce risk costs"
  ) %>% 
  detailed_entries(role, loc, company, dates, details)
```

# Education

```{r}
# Define information on data science accelerator program
DSAP_info <- c("Data Science Accelerator Program", "Go Data Driven", "2016 - 2017", "")
# Define information on Master
MSc_info <- c("MSc (Cum Laude), Transport, Infrastructure & Logistics", "Delft University of Technology", "2011 - 2014", "GPA: 8.5")
# Define information on exchange
exch_info <- c("Erasmus Exchange in Transport Science", "KTH Royal Institute of Technology in Stockholm", "2011 - 2012", "GPA: 9.3")
# Define information on Bachelor
BSc_info <- c("BSc (Cum Laude), Technical Policy Management", "Delft University of Technology", "2008 - 2011", "GPA: 8.7")
# Combine all information
tribble(
    ~ degree, ~ uni, ~ dates, ~ gpa, ~ details,
    # DSAP
    DSAP_info[1], DSAP_info[2], DSAP_info[3], DSAP_info[4], 
      "Combines in-depth and hands-on lectures with practical workshops to improve data science skills and knowledge",
    DSAP_info[1], DSAP_info[2], DSAP_info[3], DSAP_info[4], 
      "Capstone project: detect potential iPhone fraud on Marktplaats using scraped web data and images",
    # MSc
    MSc_info[1], MSc_info[2], MSc_info[3], MSc_info[4], 
      "Specialization: Engineering - Transport, Logistics & Supply Chains",
    MSc_info[1], MSc_info[2], MSc_info[3], MSc_info[4], 
      "Thesis: Continuous Risk Management of Customers, Application at the ING Arrears Department",
    MSc_info[1], MSc_info[2], MSc_info[3], MSc_info[4], 
      "Honours Programme: Swedish Transport & Logistics Systems",
    # Exchange
    exch_info[1], exch_info[2], exch_info[3], exch_info[4], 
      "Five courses during the first semester (37.5 ECTS) as part of my MSc Honours Programme",
    # BSc
    BSc_info[1], BSc_info[2], BSc_info[3], BSc_info[4], 
      "Domain: TIL - Transport, Infrastructure & Logistics",
    BSc_info[1], BSc_info[2], BSc_info[3], BSc_info[4], 
      "Minor: Entrepreneurship for Smart Living 2020 (Awarded best project)"
  ) %>% 
  detailed_entries(degree, gpa, uni, dates, details)
```
